Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-01-11 paper/paper.Rmd
checking the results from Garcia paper. They are not reproducible from what they give. Why don't they just share code/

>>>>

From extRemes package: "where shape = 0 gives rise to the exponential df (light tail), shape > 0 the Pareto df (heavy tail) and shape < 0 the Beta df (bounded upper tail at location - scale.u/shape). Theoretical justification supports the use of the GP df family for modeling excesses over a high threshold (i.e., y = x - threshold)."
